%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

	%---------------------------------------------------------
	\cventry
	{Software Engineer II} % Job title
	{Sentar Inc.} % Organization
	{San Diego, CA, USA} % Location
	{Jan. 2024 - Present} % Date(s)
	{
		\begin{cvitems}
			\item {Update code base to allow the device react to external triggers and send commands to other devices}
			\item {Update Web HMI code to support all modern browsers}
			\item {Create automated build and scan pipeline using OpenShift and Coverity}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Software Engineer II} % Job title
	{Epsilon C5I} % Organization
	{San Diego, CA, USA} % Location
	{Jun. 2023 - Dec. 2023} % Date(s)
	{
		\begin{cvitems}
			\item {Update and create automated tests using RobotFramework}
			\item {Execute manual tests for multiple products}
			\item {Maintain and troubleshoot multiple OpenShift deployments}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Jr. Software Engineer III} % Job title
	{Moebius Solutions, Inc.} % Organization
	{San Diego, CA, USA} % Location
	{Dec. 2019 - Jan. 2023} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Contributed to open source projects for the company with Python, JavaScript, TypeScript, React, and Redux.}
			\item {Deployed multiple applications for the customer using OpenShift, Docker, and Jenkins.}
			\item {Rewrote frontend for customer using modern frontend practices with TypeScript, React, and Redux.}
			\item {Documented test procedures for products in LaTeX}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Jr. Software Engineer} % Job title
	{ScoreShuttle} % Organization
	{San Diego, CA, USA} % Location
	{Jan. 2019 - May. 2019} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Added new routes to RESTful API server for credit management service.}
			\item {Create administrator tools to manage customer accounts, get better sales data, and allow for 3rd parties to be added to the service.}
		\end{cvitems}
	}

	%---------------------------------------------------------
\end{cventries}
